Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-05 manuscript/manuscript.Rmd
single column

journal: "Variance"
date: "`r Sys.Date()`"
bibliography: explain-pricing.bib
#linenumbers: true
numbersections: true
# csl: elsevier-harvard.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
layout: preprint, 3p, twocolumn, letterpaper, 10pt
---

>>>>

journal: "Variance"
date: "`r Sys.Date()`"
bibliography: explain-pricing.bib
#linenumbers: true
numbersections: true
# csl: elsevier-harvard.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
layout: preprint, 3p, letterpaper, 10pt
---
